Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-19 sections/correlated-sicm-and-fm.tex
reworked

Similar to a SICM and wide-field combination, a combination of SICM and
confocal FM enables imaging of the same region and sample with both techniques
(Fig.~\ref{fig:sicm+cfm}a). The technical implementation involves mounting a
SICM onto an inverted confocal FM. The software used to control the two
microscopes does not have to be the same as both microscopes record data
independently from one another. However, as the recordings are not
simultaneous, pixel-by-pixel correlation is hardly, if at all, possible.

@@

Seifert et al. \cite{Seifert2017} investigated the morphological activity of
platelets by time-lapse SICM and subsequently obtained confocal recordings of
cytoskeletal proteins of the investigated cells, allowing them to correlate
the activity of the platelets and the structure of the cytoskeleton.
In co-cultures of cardio-myocytes and myofibroblasts, the dynamics of
myocyte-myofibroblast connections was linked to the expression of connexin-43
\cite{Schultz2019}.

@@

A second study on neurons investigated, besides others, cargo transport in
neuronal dendrites \cite{Takahashi2019}. Here, the combination of
confocal FM and SICM provided a hint that the transport processes observed by
SICM were mediated by mitochondria.

In a study investigating the formation of human immunodeficiency virus-like
particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
to investigate topography changes together with the distribution of
fluorescently labelled viral proteins like Gag or Viral Protein R
\cite{Bednarska2020}. In contrast to investigating the virus formation with
TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal FM
allowed to investigate the apical side of the cells. It was found that the
release of VLPs is a lot faster than the release at the basal cell side as
known from TIRF investigations and furthermore, a potential impact on the
release time by the application of a fluorescent marker was found
\cite{Bednarska2020}.

>>>>

Similar to a SICM and wide-field combination, a combination of SICM and
confocal FM enables imaging of the same region and sample with both techniques
(Fig.~\ref{fig:sicm+cfm}a). Again, the technical implementation requires mounting a
SICM onto an inverted confocal FM. Two different modes of operation are
conceivable. In the first one, both microscopes record data
independently from each other and thus both microscopes can use their own
soft- and hardware to control the single components. However, pixel-by-pixel
correlation, if desired, might be impeded by different
implementations to compensate for non-linear responses of the positioning
piezo-actors in the different software. This problem might become even more
prominent if different positioning devices such as beam scanning for confocal
FM and stage scanning for SICM are used.

The second mode of operation is to record the topography and the fluorescence at each
$x, y$-position at the same time or with only a minimal temporal
offset. Technically, this requires the synchronisation of the SICM and the
confocal microscope, which at least requires a distinct software.

@@

Seifert et al. investigated the morphological activity of
platelets by time-lapse SICM and subsequently obtained confocal recordings of
cytoskeletal proteins of the investigated cells, allowing them to correlate
the activity of the platelets and the structure of the cytoskeleton
\cite{Seifert2017}.

Another investigation which correlated SICM and subsequent confocal FM
recordings studied cell-cell connections in co-cultures of cardio-myocytes and
myofibroblasts. Here, the dynamics of myocyte-myofibroblast connections was
linked to the expression of connexin-43 \cite{Schultz2019}.

@@

A second study on neurons investigated, besides others, cargo transport in
neuronal dendrites \cite{Takahashi2019}. Here, the simultaneous combination of
confocal FM and SICM provided a hint that the transport processes observed by
SICM were mediated by mitochondria.

The simultaneous recording of SICM and confocal data was used to study the
formation of human immunodeficiency virus-like particles (VLPs) together with
the dynamics of fluorescently labelled viral proteins like Gag or Viral
Protein R \cite{Bednarska2020}. In contrast to investigating the virus
formation with TIRF microscopy \cite{Jouvenet2008}, the combination of SICM
and confocal FM allowed to investigate the apical side of the cells. It was
found that the release of VLPs is a lot faster than the release at the basal
cell side as known from TIRF investigations and furthermore, a potential
impact on the release time by the application of a fluorescent marker was
found \cite{Bednarska2020}. The total height differences of the topographies
analyzed in this study were approximately in the range of the vertical
resolution of the confocal data, and thus, the data sets were not only
correlated in the horizontal, but also in the vertical direction.
